Tutorial_1

### 2024-09-17 Tutorial_1_descriptive_stats/Tutorial_1.Rmd
change filter condition

# function extract_median is used to extract the S(t).50 quantiles (i.e., the estimated median RTs)
extract_median <- function(df){
  above_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival > .5) %>% 
      slice(n()) # take last row
  below_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival < .5) %>% 
      slice(1) # take first row
  # pull period above
  period_above <- pull(above_pct50, period)
  # pull survivor function values
  survival_above <- pull(above_pct50, survival)
  survival_below <- pull(below_pct50, survival)
  # estimate median by interpolation
  median_period <- period_above+((survival_above-.5)/(survival_above-survival_below))*((period_above+1)-period_above)
}

>>>>

# function extract_median is used to extract the S(t).50 quantiles (i.e., the estimated median RTs)
extract_median <- function(df){
  above_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival >= .5) %>% 
      slice(n()) # take last row
  below_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival < .5) %>% 
      slice(1) # take first row
  # pull period above
  period_above <- pull(above_pct50, period)
  # pull survivor function values
  survival_above <- pull(above_pct50, survival)
  survival_below <- pull(below_pct50, survival)
  # estimate median by interpolation
  median_period <- period_above+((survival_above-.5)/(survival_above-survival_below))*((period_above+1)-period_above)
}
